Pteropod exposure analysis

### 2018-03-16 expose.Rmd
better model sel input for expose

```{r}
selectInput("mod", "Choose model:", paste0('mod', seq(1:nrow(mod_all))))

@@

  md <- filter(mod_all, Model %in% input$mod) %>% 
  .$Modobj %>% 
  .[[1]]

>>>>

```{r}
sellab <- env_cmb %>% 
  bind_cols(md = paste0('mod', seq(1:nrow(mod_all))), .) %>% 
  unite('vr', trt, res, X1, X2, sep = ', ') %>% 
  unite('vr2', md, vr, sep = ': ') %>% 
  unlist %>% 
  as.character

selectInput("mod", "Choose model:", sellab)

@@

  tosel <- strsplit(input$mod, ':')[[1]][1]

  md <- filter(mod_all, Model %in% tosel) %>% 
  .$Modobj %>% 
  .[[1]]
